% \section{Introduction}
% \subsection{Purpose}
% \subsection{Scope}
% 
% \section{Test Environment \& Conditions}
% 
% %This section should contain items such as testing tools and suites, runtime environments, OS, etc.
% 
% \section{Test Procedures \& Results}
% 
% \subsection{Test 1}
% \subsubsection{Description}
% \subsubsection{Pre-Conditions}
% \subsubsection{Post-Conditions}
% \subsubsection{Inputs}
% \subsubsection{Outputs}
% 
% %More tests go here 
% 
% \section{Test Summary}
% %This section provides a summary of the test scope and results. A table should be provided of all the tests conducted with an indication of pass/fail.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%% GUIDELINES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%	Make the plan concise. Avoid redundancy and superfluousness. 
% 	If you think you do not need a section that has been mentioned 
% 	in the template, go ahead and delete that section in your 
% 	test plan.
% 	
% 	Be specific. For example, when you specify an operating system 
% 	as a property of a test environment, mention the OS Edition/Version 
% 	as well, not just the OS Name.
%  	
%	Make use of lists and tables wherever possible. Avoid lengthy 
% 	paragraphs.
% 
%	Have the test plan reviewed a number of times prior to baselining 
% 	it or sending it for approval. The quality of your test plan speaks 
% 	volumes about the quality of the testing you or your team is going to 
% 	perform.
% 	
%	Update the plan as and when necessary. An out-dated and unused 
% 	document stinks and is worse than not having the document in the 
% 	first place.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
The functions within the Reporting module in the Research Support System will be tested with unit tests to determine whether the pre and post conditions specified in the service contracts were met by the module. A plan of said tests are provided in this report. The non functional requirements of the system will also be tested/ evaluated and are also described in this report. 
\subsection{Purpose}
The purpose of this document is to give an overview of the test plan for the reporting module. This document will outline the approaches used to test the module. Functional as well as non-functional requirements will be tested. This document will give an indication as to how well the reporting module of the system performs. It will also provide a list of functionalities to be tested and their respective results. This test plan will focus on the requirements outlined in the software requirements specification(SRS) instead of the requirements implamented in the reporting module. 
\subsection{Scope}
\begin{enumerate}
%Needs to be updated according to final structure
	\item Provide an overview of the test plan.
		
The remainder of this document is structured as follows. It will give references to related documents. This document will   list the features to be tested for both functional and non-functional requirements, it will also list features that will not be tested and reasons thereof. The approach to testing will be mentioned, the passing and failing of tests will be given and for all tests the respective suspension and resumption criteria will be stated. References to supporting work on this test plan will be supplied. The test environment will be outlined. Test efforts/costs will be estimated. The training of staff involved to use the system will be mentioned and the responsibilities of the different users will be mentioned. The risks involved in using this system as well as contingency plans will be given. Assumptions and dependencies of this test plan will be mentioned, and the approvers of this test plan will be listed.

	\item Specify the goals/objectives.

The goal of this test plan is to identify possible flaws in the implementation of the reporting module. If flaws are found they will be detailed in this report. The aim would then be for the implementers to either complete unmet requirements or to fix the implementation of identified incorrect code.

	\item Specify any constraints.

The constraints of developing a test plan for this module is the vague documentation of this module given in the SRS. 
\end{enumerate} 
\section{References} 
\hypersetup{
	linkcolor = blue       
}   
The master specification for the system in question resides \href{https://clickup.up.ac.za/bbcswebdav/pid-791422-dt-content-rid-8256558_1/xid-8256558_1}{here} and will be referenced throughout this document.

\section{Test Items}
The object under test is the Reporting module in version 1.0 of the Research Support System.

\section{Features to be Tested}

The features to be tested are divided into functional and non-functional tests. The aspects that will be tested and evaluated in these tests are described in the following sections. 
Describe the overall approach for the level of testing. For each major feature or group of features,
specify the approach that will ensure that they are adequately tested. The approach may be described in
sufficient detail to permit identification of the major testing tasks and estimation of the time required to
do each one.\\\\ 

\subsection{Functional}
The approach taken for the functional requirements testing is a black box testing approach. This means that the functionality of the application is tested without considering the internal implementation. Hence, one is aware of what the specific module should be able to accomplish but not how the module accomplishes it. Test cases are established based on the Software Requirements Specifications and the pre and post conditions for the Reporting module. Both negative and positive tests will be conducted. There are two main services, firstly to generate a report based on the progress status of the publications and secondly to create a report with information regarding all accreditation units active within a specified time period. Tests will be created to test whether the Reporting module performs the right functions to provide these services accurately. 

\begin{tabular}{ l|l|l|l } 
	\hline
	\textbf{Feature ID} & \textbf{SRS Source} & \textbf{Summary} & \textbf{Test Case ID}\\
	\hline
	\hline
	getAccreditationPointsReport & Section x.y & This service  &\begin{tabular}[t]{@{}l@{}}
		TC01\\
		TC02\\
		TC03\\		
	\end{tabular}\\
	\hline
	getProgressReport & Assumed & short descriptinon & TC04\\
	\hline
	\hline
\end{tabular}	

\subsection{Non-Functional}
\begin{enumerate}
\item For the non-functional testing, firstly the code will be evaluated to see whether there is flexibility in terms of the reporting framework used i.e. that the application functionality is not tied to one specific technology. In addition, the persistence provider should also be easily modifiable. 
\item The maintainability of the code will be evaluated in terms it being easy to understand by future developers who would work on the system. In addition, developers should be able to add and modify the functions in the classes with ease. The technologies chosen for the project will also be evaluated to ensure that they will still be available for a reasonable amount of years following the deployment of the application.
\item The system should be reliable and provide a deployment without single points of failure. Reliability of this module will be evaluated 
\item The testability of the system will be examined by mainly detecting the use of mock objects and automated unit and integration tests. These tests will further be examined as to whether they test whether the service contract in the specification was adhered to.
\item The deployability of the module will be evaluated to see whether the application could be deployed on an application server.
\end{enumerate}
\section{Features not to be Tested}
Features that are excluded from this test plan include:
\begin{itemize}
	\item Features in modules outside of the Reporting module.
	\item Performance
	\item Scalability
\end{itemize}

For this level of testing, modules were allocated to different teams and therefore this testing activity is restricted to one module. Since the focus is only on verification of requirements, several important non-functional requirements that did not feature in the SRS are also not going to be tested.

\section{Test Identification}
\begin{itemize}
	\item  Objective - Identify and briefly describe the special focus or objective for the test case or a series of test cases.
This is much more detailed than the Test Items in the Level Test Plan. It may include the risk or priority for this particular test case or series of test cases.
	\item  Inputs - Specify each input required to execute each test case. Some inputs will be specified by value (with
tolerances where appropriate), whereas others, such as constant tables or transaction files, will be
specified by name. Identify all appropriate databases, files, terminal messages, memory resident areas,
and values passed by the operating system.
	\item  Outcome(s) - Specify all outputs and the expected behavior (e.g., response time) required of the test items. Provide
the exact value (s) (with tolerances where appropriate) for each required output and expected behavior.
This section is not required for self-validating tests.
\end{itemize}

Which we can again tabulate if you want: \\\\
\begin{tabular}{ L{3cm}| L{3cm}| L{3cm}| L{3cm}| L{0cm}} 
	\hline      
	\textbf{Test Case ID} & \textbf{Objective} & \textbf{Inputs} & \textbf{Outcome}\\
	\hline 
	\hline
	View Research Group Report  &  
	The objective for this test case is to test that a report can be generated for a specific research group that the user can specify on the form & 
	The inputs required to execute this test case are the user's selection of a particular research group. This is an optional field and if it is not selected, a report will be generated for the entire department. & 
	The outcome of this test case should be that a report is generated for the specified research group & \\
	\hline 
View Report For Specific Lifecycle State  &  
	The objective for this test case is to test that a report can be generated for a specific life cycle state that the user can select on the form. A lifecycle state refers to the current status of the paper i.e. accepted, submitted, published. Hence a report will be generated displaying the papers of the selected state only & 
	The inputs required to execute this test case are the user's selection of a particular lifecycle state. This is an optional field and if it is not selected, a report will be generated including all utilized states . & 
	The outcome of this test case should be that a report is generated for the specified lifecycle state & \\ 
	\hline 
View Department Report &  
	The objective for this test case is to test that a report can be generated for the entire research department.This will also be the default option if users do not select filter options & 
	The inputs required to execute this test case are the user's selection of the option to view report, without selecting filters. & 
	The outcome of this test case should be that a report is generated for the entire department& \\ 
\end{tabular}
\\
\begin{tabular}{ L{3cm}| L{3cm}| L{3cm}| L{3cm}| L{0cm}} 
\hline 
View Report For Specific Publication Type &  
The objective for this test case is to test that a report can be generated for a specific publication type that the user can select on the form. A publication type refers to either a conference paper, journal article or technical papers. Hence a report will be generated displaying the papers of the selected specific publication type & 
	The inputs required to execute this test case are the user's selection of a particular publication type. This is an optional field and if it is not selected, a report will be generated including all utilized publication types . & 
	The outcome of this test case should be that a report is generated for the specified publication type& \\ 
\hline 
View Report For Specific Time Frame &  
The objective for this test case is to test that a report can be generated for a specific time frame that the user can select on the form. & 
	The inputs required to execute this test case are the user's selection of a particular time frame. This is an optional field and if it is not selected, a report will be generated for the entire period. & 
	The outcome of this test case should be that a report is generated for the specified time frame& \\ 
\hline
View Report For Specific Person &  
The objective for this test case is to test that a report can be generated for a specific person, provided the name and surname of said person is entered on the form & 
	The inputs required to execute this test case are the name and surname of the person for whom the report should be generated& 
	The outcome of this test case should be that a report is generated for the specified person& \\ 
\hline	 
\end{tabular}

\subsection{View Research Group Report}
\subsubsection{Objective}
This test case will evaluate the module's functionality specific to the generation of a research group report, containing all the relevant information, where the group is specified by a user.

\subsubsection{Input}
The user may specify a research group identity. This field is optional.

\subsection{Outcome}
Where the user specifies a research group,  a report for that group should be generated. 
Where the user omits this field, a report for the entire department should be generated.

\subsection{View Report For A Specific LifeCycleState}
\subsubsection{Objective} \label{TC_LifeCycleState_Obj}
This test case will evaluate the module's functionality for the generation of reports on research in a specific LifeCycleState. The LifeCycleState of some project may be one of the following:
\begin{itemize}
	\item InProgress
	\item Submitted
	\item Accepted
	\item InRevision
	\item Published
	\item Abandoned
\end{itemize}
\subsubsection{Input}
The user may specify any of the LifeCycleStates mentioned in \ref{TC_LifeCycleState_Obj}. 
This field is optional and may be omitted. Any other input is invalid.

\subsection{Outcome}
Where the user specifies a valid LifeCycleState, a report should be generated where the included records are only of the specified LifeCycleState. 
Where the LifeCycleState is omitted, a report containing all projects (with any LifeCycleState) should be generated.

\subsection{View Department Report}
\subsubsection{Objective}
This test case evaluates the functionality responsible for departmental report generation

\subsubsection{Input}
\subsection{Outcome}

\subsection{View Report For A Specific Publication Type}
\subsubsection{Objective}
\subsubsection{Input}
\subsection{Outcome}

\subsection{View Report For A Specific Time Frame}
\subsubsection{Objective}
\subsubsection{Input}
\subsection{Outcome}
\section{Item Pass/Fail Criteria}


\section{Item Pass/Fail Criteria}


\section{Test Deliverables}

\begin{enumerate}
	\item List test deliverables, and links to them if available, including the following:

\begin{enumerate}
	\item Test Plan (this document itself)
	\item Test Cases 
	\item Test Reports
\end{enumerate}
\end{enumerate}
~
\section{Test Environment}

I assigned this section to Paul because he spotted a nice way of doing this portrayed in the Sample Master Plan document:P

\begin{enumerate}
	\item The properties of test environment: hardware, software, network etc.
	\item Web Server - no server used in the code provided
	\item Database - no database used in the code provided
	\item OS - Linux, Windows, IoS etc.
	\item Browser - All browsers
	\item Java Version - version 7
	\item Testing Framework - JUnit
	\item List any testing or related tools.
	\item JUnit - The unit testing framework that will be used to test functional requirements
\end{enumerate}

\section{Risks}
	The following potential risks are found in this module:
\begin{enumerate}
	\item Aggregating data for those whose names are incoherent from publication to publication.
	\item Values  which are out of bounds.
	\item Database is in an unusable state.
	\item Too much data to process at once.
\end{enumerate}

	The following are contingencies which could be used to prevent the potential risks from arising:
\begin{enumerate}

	\item Do a smart lookup on names and research groups.
	\item Always do bounds checking.
	\item Check that the database is in a stable state before attempting to access it.
	\item Use a map-reduce if necessary.
         

\end{enumerate}


\section{Assumptions and Dependencies}

\begin{enumerate}
	\item The first assumption is that the Jasper Report generated by the module consists of tables with columns for the name of person/group, publication name, publication type, organization associated with publication type, lifecycle state.
	\item The second assumption is that the module abides by the service contracts and implements the services as specified in the service contracts. In addition, we assume the pre and post conditions for the module hold and hence these will be tested.
	\item The first dependency is that since Java EE was used for implementation, a Java testing framework will be used for the tests
\end{enumerate}